Title of the paper

### 2021-08-27 paper/paper.tex

\author{%
  First name Last name\affil{1}, First name Last name\affil{2} and First name
  Last name\affil{3,}\corrauth}

@@

\address{%
  \addr{\affilnum{1}}{College of Computing and Software Engineering, Kennesaw
    State University, 1000 Chastain Road, Kennesaw, GA 30144, USA; email}
  \addr{\affilnum{2}}{Affiliation email} \addr{\affilnum{3}}{Affiliation email}}
% corresponding author
\corraddr{Email address of corresponding author; Tel: +1-111-111-1111; Fax:\\
  +1-111-111-1111.}

@@

\begin{abstract}
  An abstract is normally of 150 to 250 words. List 4 to 8 keywords all with
  lowercase (except special cases) for both highlighting the focuses of your
  study and indexing/searching in databases. Article type can be one of the
  following: regular article, case study, express letter, review or overview,
  survey, opinion, perspective, communication, lecture notes, tutorial notes,
  and editorial (special issue only).

@@

\keywords{(4 to 8 keywords)}

@@

Once a submission is received, the receiving Editor will pre-screen the article
for its suitability and quality for the journal. After passing this
pre-screening, the Editor may act as the “Academic Editor” or assign this
manuscript to another Editor from the Editorial Board as the “Academic Editor”
to handle the review of this paper, communicate with the authors on revisions,
and inform the final decision after consultation with the relevant
Editor-in-Chief.

@@

\section{Reference style, citation, and cross-reference}
Test citation \cite{Jensen1996}.

>>>>

\author{%
  Noah Gardner\affil{1} and Chih-Cheng Hung\affil{1}\corrauth}

@@

\address{%
  \addr{\affilnum{1}}{College of Computing and Software Engineering, Kennesaw
    State University, 1000 Chastain Road, Kennesaw, GA 30144, USA; email}
  % \addr{\affilnum{2}}{Affiliation email}
}
% corresponding author
\corraddr{chung1@kennesaw.edu}

@@

\begin{abstract}
  There is a large variety of ant species, and most species are diverse in terms
  of size, shape, behaviors, and especially skin (cuticle) textures. However,
  the significance of ant cuticle texture is not widely researched. This
  research employs modern machine learning methods such as texture analysis and
  classification with CNN and clustering to automatically group similar ant
  species to allow for the study of influences cuticle texture on ant
  ecology.

@@

\keywords{Texture Analysis, Image Processing, Clustering, Machine Learning,
  Myrmecology, Ecology}

@@

Once a submission is received, the receiving Editor will pre-screen the article
for its suitability and quality for the journal. After passing this
pre-screening, the Editor may act as the “Academic Editor” or assign this
manuscript to another Editor from the Editorial Board as the “Academic Editor”to
handle the review of this paper, communicate with the authors on revisions, and
inform the final decision after consultation with the relevant Editor-in-Chief.

@@

\section{Reference style, citation, and cross-reference}
Test citation \cite{ward_phylogeny_2014}.
